### 2022-11-05 rmd/nhanes_data.Rmd
stats shown; stringr dropped

data_to_doc <- nhanes_key %>% 
 .[class %in% names(classes)] %>%
 .[variable != 'svy_subpop_chol'] %>% 
 .[variable != 'svy_weight_cal'] %>% 
 .[, class := factor(class, levels = names(classes))] %>% 
 .[order(class)] %>% 
 droplevels()

data_to_doc$description %<>% stringr::str_replace_all('\u2265', '>=')
data_to_doc$label %<>% stringr::str_replace_all('\u2265', '>=')

key_classes <- split(data_to_doc, f = data_to_doc$class)

@@

 for(j in seq_along(key_classes[[i]]$variable)){
  cat("##", key_classes[[i]]$variable[j], "\n")
  cat("- Label: ", key_classes[[i]]$label[j], "\n")
  cat("- Description: ", key_classes[[i]]$description[j], "\n\n")
 }

>>>>

data_to_doc <- nhanes_key %>% 
 .[class %in% names(classes)] %>%
 .[variable != 'svy_subpop_chol'] %>% 
 .[variable != 'svy_weight_cal'] %>% 
 .[, class := factor(class, levels = names(classes))] %>% 
 .[order(class)] %>% 
 droplevels() %>% 
 .[, description := gsub('\u2265', '>=', x = description, fixed = T)] %>% 
 .[, label := gsub('\u2265', '>=', x = label, fixed = T)]

key_classes <- split(data_to_doc, by = 'class')

@@

 for(j in seq_along(key_classes[[i]]$variable)){
  cat("##", key_classes[[i]]$variable[j], "\n")
  cat("- **Label**: ", key_classes[[i]]$label[j], "\n")
  cat("- **Description**: ", key_classes[[i]]$description[j], "\n")

  if(names(key_classes)[i] != 'Survey'){
   cat(get_variable_summary(key_classes[[i]]$variable[j],
                            data = nhanes_data[svy_subpop_htn == 1]),
       "\n\n")
  } else {
   cat("\n")
  }
